Baseline centering problem

### 2018-11-29 paper/tangotd.tex

In the reversible case, $\mu\Delta$ is symmetric. We can use the
Dirichlet form which amounts to $L\deq\mu(\mu\Delta)^{-1}\mu$; then
$L\Delta=\mu$ and we have to prove that $\mu\Phi B\transp{\Phi}\rho$ is
positive.  On-policy, $\rho=\mu$ and this is obviously true, for any
positive $B$. Thus, in the reversible case, nonlinear TD converges
on-policy, for any $B$.

In the non-reversible case, let $\mu\Delta=S+A$ with $S$ symmetric and
$A$ antisymmetric. Let $L\deq \mu S^{-1} \mu$. Then we have to prove that
$\mu S^{-1} \mu \Delta \Phi B\transp{\Phi}\rho$ is positive. For any
function $f$,
\begin{align}
\transp{f} \mu S^{-1} \mu \Delta \Phi B\transp{\Phi}\rho f
&=\transp{f} \mu S^{-1} (S+A) \Phi B\transp{\Phi}\rho f
\\&=\transp{f} \mu \Phi B\transp{\Phi}\rho f + \transp{f} \mu S^{-1}
A \Phi B\transp{\Phi}\rho f
\end{align}

Let us consider the on-policy case. Then the first term is $\transp{f}
\mu \Phi B\transp{\Phi}\rho f$ and is always positive. For the second
term, since $A$ is antisymmetric, we have $\transp{x}Ax=0$ for all $x$.
Thus, we can add any multiple of $\transp{x}Ax=0$; let us take
$x=S^{-1}\mu f$:
\begin{equation}
\transp{f} \mu S^{-1}
A \Phi B\transp{\Phi}\mu f=
\transp{f} \mu S^{-1}A (S^{-1}-\Phi B\transp{\Phi})\mu f
\end{equation}

@@

Thus we have a two-timescale algorithm for non-linear TD in the on-policy
overparameterized case.

>>>>

In the reversible case, $\mu\Delta$ is symmetric.\footnote{$\rho \Delta$
can be symmetric if and only if $\rho=\mu$. Indeed, if $\rho \Delta$ is
symmetric then $\rho=\rho'$ and $\rho$ is the stationary distribution.} We can use the
Dirichlet form which amounts to $L\deq\mu(\mu\Delta)^{-1}\mu$; then
$L\Delta=\mu$ and we have to prove that $\mu\Phi B\transp{\Phi}\rho$ is
positive.  On-policy, $\rho=\mu$ and this is obviously true, for any
positive $B$. Thus, in the reversible case, nonlinear TD converges
on-policy, for any $B$.

In the non-reversible case, let $\rho\Delta=S+A$ with $S$ symmetric and
$A$ antisymmetric. Let $L\deq \rho S^{-1} \rho$. Then we have to prove that
$\rho S^{-1} \rho \Delta \Phi B\transp{\Phi}\rho$ is positive. For any
function $f$,
\begin{align}
\transp{f} \rho S^{-1} \rho \Delta \Phi B\transp{\Phi}\rho f
&=\transp{f} \rho S^{-1} (S+A) \Phi B\transp{\Phi}\rho f
\\&=\transp{f} \rho \Phi B\transp{\Phi}\rho f + \transp{f} \rho S^{-1}
A \Phi B\transp{\Phi}\rho f
\end{align}

The first term $\transp{f}
\rho \Phi B\transp{\Phi}\rho f$ is always positive. For the second
term, since $A$ is antisymmetric, we have $\transp{x}Ax=0$ for all $x$.
Thus, we can add any multiple of $\transp{x}Ax=0$; let us take
$x=S^{-1}\rho f$:
\begin{equation}
\transp{f} \rho S^{-1}
A \Phi B\transp{\Phi}\rho f=
\transp{f} \rho S^{-1}A (S^{-1}-\Phi B\transp{\Phi})\rho f
\end{equation}

@@

Thus we have a two-timescale algorithm for non-linear TD in the off-policy
overparameterized case.

(Still works for non-overparameterized if $A$ does not couple the image
of $\Phi$ and its complement...)
